---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) 
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
1. **How has the rate of tree planting changed across years?**
2. **How does tree planting correlate with seasonality? Are more trees planted in certain months or seasons?**
3. **Are some neighborhoods more diverse in their range of tree species than others?**
4. **Are certain tree species more prevalent in specific neighborhoods?**
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->
## **How has the rate of tree planting changed across years?**
To address this question, we will begin by computing the range, mean, standard deviation and median overall rate of tree planting (trees planted per year) in the `vancouver_trees` data set (task 1). This will give me an understanding of the overall rate of tree planting, following which we will plot a graph of rate of tree planting per year to see which years was planting more successful than others. This graph will have at least two geom layers to indicate both the individual year's planting rate (geom_point()) as well as the trend in planting rate over time (geom_line()) (task 8). 

#### Summarizing:
```{r}

   tree_planting_by_year <- vancouver_trees %>%
      mutate(year_planted = year(date_planted)) %>%
      group_by(year_planted) %>%
      filter(!is.na(year_planted)) %>% 
      summarize(total_trees = n())

  tree_planting_by_year 

  summary_stats <-  tree_planting_by_year %>%
                    summarize(
                      range_min = min(total_trees),
                      range_max = max(total_trees),
                      mean_planting_rate = mean(total_trees),
                      sd_planting_rate = sd(total_trees),
                      median_planting_rate = median(total_trees)
                      )

  summary_stats #display the summary statistics


```

### Graphing:
```{r}
  
  ggplot(tree_planting_by_year, aes(x = year_planted, y = total_trees)) +
    geom_line() +
    geom_point() +
    xlab("Year") +
    ylab("Total Trees Planted") +
    ggtitle("Rate of Tree Planting Across Different Years") +
    theme_minimal() +
    coord_cartesian(ylim = c(0, 10000))

```

## **How does tree planting correlate with seasonality? Are more trees planted in certain months or seasons?**
To address this question, we will begin by creating a "season variable (categorical) (task 3). I will be extracting month information from the `date_planted` variable in the `vancouver_trees` data set and have defined the seasons as listed in the table below:

Number  | Month   | Season
------  | ------  | --------
1   | January | Winter
2   | February | Winter
3   | March | Spring
4   | April | Spring
5   | May | Spring
6   | June | Summer
7   | July | Summer
8   | August | Summer
9   | September | Fall
10   | October | Fall
11   | November | Fall
12   | December | Winter

We will then graph the number of trees planted per year, using separate lines for each season and customizing the alpha transparency so that the patterns in tree planting trends per season are more easily visualized (task 7).

### Summarizing: 
```{r}

#creating a new "season" column
#the Spring, Summer, Fall or Winter label is assigned to each row (tree) based on the month it was planted
trees_planted_by_year <- vancouver_trees %>%
  filter(!is.na(date_planted)) %>% 
  mutate(month_planted = month(date_planted),
         season = case_when(month_planted %in% c(3, 4, 5) ~ "Spring",
                            month_planted %in% c(6, 7, 8) ~ "Summer",
                            month_planted %in% c(9, 10, 11) ~ "Fall",
                            month_planted %in% c(12, 1, 2) ~ "Winter", 
                            TRUE ~ "Unknown")) %>%
  mutate(year_planted = year(date_planted)) %>%
  group_by(season, year_planted) %>%
  summarize(total_trees = n())

  trees_planted_by_year

```

### Graphing:
```{r}

  trees_planted_by_year %>%
    ggplot(aes(year_planted, total_trees)) +
    geom_line(aes(colour = season), alpha = 0.5) +
    xlab("Year") +
    ylab("Trees Planted") +
    ggtitle("Rate of Tree Planting Across Different Years") +
    theme_minimal() +
    coord_cartesian(ylim = c(0, 2000))
```

In the graph above, we can see that across the years it is most common for majority of trees to be planted in the Winter season. However, there is an interesting decreasing trend of trees planted in the winter since 2013 - perhaps, this may be due to more severe and colder winters over more recent years. This could be worth exploring in the future. 

## **Are some neighborhoods more diverse in their range of tree species than others?**
First we will compute the number of unique tree species and number of total trees in each neighbourhood (task 2). We will also calculate a diversity ratio defined by the number of unique tree species divided by the number of total trees per neighbourhood. Then, we will graph different bar charts to show these trends and ensure the theme and axes are adjusted to make the charts readable and pretty (task 6).

### Summarizing:
```{r}
  #Counting unique species and total trees per neighborhood:
  tree_diversity_per_neighborhood <- vancouver_trees %>%
    group_by(neighbourhood_name) %>%  
    summarise(unique_species = n_distinct(species_name), total_trees_per_neighbourhood = n(), diversity_ratio = unique_species / total_trees_per_neighbourhood * 100)

    tree_diversity_per_neighborhood

```

### Graphing:
```{r}

  ggplot(tree_diversity_per_neighborhood, aes(x = neighbourhood_name, y = unique_species)) +
  geom_bar(stat="identity") +
  theme_minimal() +
  labs(title = "Tree Species Diversity by Neighborhood",
       x = "Neighborhood",
       y = "Unique Species Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

  ggplot(tree_diversity_per_neighborhood, aes(x = neighbourhood_name, y = total_trees_per_neighbourhood)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    labs(title = "Total trees by Neighborhood",
         x = "Neighborhood",
         y = "Total trees") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
   ggplot(tree_diversity_per_neighborhood, aes(x = neighbourhood_name, y = diversity_ratio)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    labs(title = "Diversity ratio by Neighborhood",
         x = "Neighborhood",
         y = "Ratio of unique species to total trees") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

## **Are certain tree species more prevalent in specific neighborhoods?**

To answer this question we will focus on understanding the prevalence of Maple tree species (Acer genus) in different neighbourhoods as the full `vancouver_trees` data set is rather large and we were focusing milestone 1 on maple trees as well. I will first compute the number of Acer trees in each species across the different neighbourhoods (task 2). I will then plot these data in separate bar charts for each neighbourhood. To visualize certain species of Maple tree across Vancouver neighbourhood, I will also plot these trees on a location map (longitude vs latitude) and adjust the alpha transparency to make sure it is readable (task 7).

### Summarizing:
```{r}
 
 # Group by neighborhood and tree species to count the number of each species in each neighborhood
  species_by_neighborhood <- vancouver_trees %>%
    filter(!is.na(neighbourhood_name) & !is.na(genus_name) & genus_name == "ACER") %>%  # Remove rows where either of these is NA
    group_by(neighbourhood_name, species_name) %>%  
    summarise(count = n())  # count occurences

  species_by_neighborhood
  
  vancouver_trees
  
```

### Graphing:
```{r fig.width=20, fig.height=60}  

    # Plotting this information:
    ggplot(species_by_neighborhood, aes(x = species_name, y = count)) +
      geom_bar(stat = "identity") +
      facet_wrap(~ neighbourhood_name, scales = "free", ncol = 2) +  
      xlab("Tree Species") +
      ylab("Count") +
      ggtitle("Prevalence of Tree Species by Neighborhood") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

As I described above, it would also be interesting to graph the distribution of Maple trees (Acer genus) in a visual manner. Let's use longitude and latitude information of each tree to do so. For the purpose of this exercise, let's focus on Acer rubrum (Red Maple tree) as we can see in the plots above that they are a fairly common species of Maple tree across all Vancouver neighbourhoods.

```{r fig.width=12, fig.height=5}

  # In this graph, we will colour by neighbourhood_name and use size of the point to reflect the tree diameter
  vancouver_trees %>%
    filter(genus_name == "ACER", species_name == "RUBRUM") %>%
    ggplot(aes(x = longitude, y = latitude)) +
    geom_point(aes(colour = neighbourhood_name, size = diameter), alpha = 0.25)

```

From the first milestone assignment (MDA1), we learned that Acer rubrum and Acer platanoides are the most prevalent types of Maple trees in Vancouver neighbourhoods. Let's also plot these visually on the longitude vs latitude graph:

```{r fig.width=12, fig.height=5}

  # Let's plot these two tree types and colour by tree species to visualize their distribution as we did above:
  vancouver_trees %>%
    filter(genus_name == "ACER", species_name == "RUBRUM"| species_name == "PLATANOIDES") %>%
    ggplot(aes(x = longitude, y = latitude)) +
    geom_point(aes(colour = species_name, size = diameter), alpha = 0.25)

```

Interesting, we see more Acer rubrum trees on the west side of Vancouver while there are more Acer platanoides on the east side. I wonder whether this is due to soil conditions or a different factor. 

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->

The first two questions have been fully addressed: (1) by visualizing the trends in total tree planting in Vancouver across years, we noticed a drop in tree planting after 2013 and (2) by plotting the relationship between seasonality and tree planting, we learned that generally trees are planted in the Winter months in Vancouver which is interesting and likely different across Canada, especially in areas such as Alberta where it snows and the ground tends to freeze over. This is cool! 

The remaining two questions explored tree diversity and distribution across various Vancouver neighbourhoods. While we have begun to get an understanding of tree diversity and the distribution of Maple trees (Acer genus) across Vancouver, there are more neighbourhood specific patterns we can explore - such as which neighbourhoods have the largest trees, which plant the most trees, etc. 

<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->

The `vancouver_trees` data set contains tidy data as each row represents one tree (observation), each column is a variable by which to describe this tree and each cell contains just one value. Refer to the list below for a description of why 8 randomly selected variables from this data set demonstrate that the data is tidy:

-   `tree_id` - a quantitative variable, each indexed row (tree observation is assigned a specific numeric value to serve as a tree identifier
-   `genus_name` - a character variable, each indexed row (tree observation) is assigned to a specific genus name
-   `species_name` - a character variable, each indexed row (tree observation) is assigned to a specific species name
-   `on_street` - a character variable, each indexed row (tree observation) is associated with a specific street 
-   `neighbourhood_name` - a character variable, each indexed row (tree observation) is located in a specific neighbourhood 
-   `height_range_id` - a numeric variable, each indexed row (tree observation) is assigned a height ID
-   `diameter` - a numeric variable, each indexed row (tree observation) has a defined tree diameter
-   `date_planted` - a date variable, each indexed row (tree observation) has a specific date on which the tree was planted

<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

We will use the pivot_wider function to untidy this data set. I am particularly interested in investigating neighbourhood specific patterns in tree planting, such as the tree type differences across Vancouver communities. To transform `vancouver_trees` into untidy data to address this question, we will begin by grouping by neighbourhood_name and summarizing the number of each tree type (using common_name of trees here) in each neighbourhood. As you can see below, now each row represents a unique neighbourhood name and there is a new column for each common tree name containing the number of that specific tree in the neighbourhood. **This makes the data untidy since each row now holds combined counts of multiple trees (no longer one observation per row).**

```{r}

  untidy_data_wider <- vancouver_trees %>%
    group_by(neighbourhood_name, common_name) %>%
    summarize(count = n(), .groups = 'drop') %>%
    pivot_wider(names_from = common_name, values_from = count, values_fill = 0)

  untidy_data_wider

```

Now, to tidy the data set again, we will use the pivot_longer function. **This transforms the untidy dataset back into a tidy format**, where each row represents a unique observation characterized by neighbourhood_name, common_name and a count variable that lists the number of trees of each type in that neighbourhood. 

```{r}

    tidy_data <- untidy_data_wider %>%
      pivot_longer(cols = -neighbourhood_name, 
                   names_to = "common_name", 
                   values_to = "count") %>%
      filter(count > 0)
    
    tidy_data

```

<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  **Which neighbourhood planted the most and least number of trees?**

2. **How have the neighbourhood-specific tree planting trends changed over time?**

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

I chose the above two research questions as we learned in the initial analysis in task 1 that the trends in tree planting have decreased in recent years (a decrease in number of trees planted per year since 2013). I would like to understand if this is neighbourhood-specific or a general trend across all neighbourhoods in Vancouver.

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below --------------------------->

## Question 1: Which neighbourhood planted the most number of trees?

```{r}

  #Identify the neighbourhood with the most and least trees
  tree_count_arranged <- vancouver_trees %>%
  filter(!is.na(neighbourhood_name)) %>% #filter out missing values
  group_by(neighbourhood_name) %>% 
  summarize(tree_count = n()) %>% #drop irrelevant columns, only retain neighbourhood_name and tree_count
  arrange(tree_count) #arranges rows from lowest to highest tree count

  print(tree_count_arranged) 
  #top row is the neighbourhood with least trees planted
  #last row is the neighbourhood with the most trees planted
  
```

## Question 2: How have these trends changed over time?
```{r}  
  vancouver_trees
  # Create another table containing the number of trees planted each year in each neighborhood
  trees_over_time <- vancouver_trees %>%
    mutate(year_planted = year(date_planted)) %>% 
    group_by(year_planted, neighbourhood_name) %>% 
    summarize(tree_count = n()) #only retain year_planted, neighbourhood_name and tree_count columns
  
  print(trees_over_time)
  
```
  
```{r fig.width=12, fig.height=5}
    
   # Plotting the trend over time
    ggplot(trees_over_time, aes(x = year_planted, y = tree_count, color = neighbourhood_name)) +
      geom_line(alpha = 0.25) +
      ggtitle("Tree Planting Trends Over Time by Neighborhood") +
      xlab("Year") +
      ylab("Number of Trees Planted") +
      coord_cartesian(ylim = c(0, 600))

```

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: How has the rate of tree planting in different neighbourhoods changed across years?

**Variable of interest**: Number of Trees Planted (tree_count)

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expct you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->


```{r}
  
  trees_per_year_fairview <- vancouver_trees %>%
    mutate(year_planted = year(date_planted)) %>%
    filter(!is.na(year_planted) & neighbourhood_name == "FAIRVIEW") %>%
    group_by(year_planted) %>%
    summarise(tree_count = n()) %>%
    arrange(year_planted)

  trees_per_year_fairview

  model <- lm(tree_count ~ year_planted, data = trees_per_year_fairview)
  
  # Print the output of the model
  summary(model)

```

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.

<!-------------------------- Start your work below ---------------------------->

I am going to use the fitted model to predict how many trees will be planted in the Fairview neighbourhood in the next three years (2024, 2025 and 2026). As shown below, the linear model predicted that approximately 38 trees would be planted per year in the next three years in Fairview.

```{r}

    # Create a data frame with future years
    future_years <- data.frame(year_planted = c(2024, 2025, 2026))
  
    # Make predictions
    predictions <- predict(model, newdata = future_years)
  
    # Combine future years and predictions into a tibble
    future_predictions <- tibble(year_planted = future_years$year_planted, predicted_tree_count = predictions)
    
    future_predictions

```


<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

```{r}

  #install.packages("here")
  library(here)

  write.csv(tree_diversity_per_neighborhood, here("output", "tree_diversity_per_neighborhood.csv"))

```

<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->

```{r}

  saveRDS(model, here("output", "model_object.rds"))

  loaded_model <- readRDS(here("output", "model_object.rds"))
  loaded_model

```

<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.