---
title: "Mini Data-Analysis"
author: "Maggie Chopra"
date: "2023-09-28"
output: md_document
---
# Mini Data-Analysis (STAT545A)

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

    ```{r}
      #remove the hashtag ('#') symbol before the lines of code you wish to run below:
      #install.packages("devtools")
      #devtools::install_github("UBC-MDS/datateachr")
    ```

2. Load the packages below.

    ```{r}
    library(datateachr)
    library(tidyverse)
    ```

3. Make a repository in the <https://github.com/stat545ubc-2023> Organization. You can do this by following the steps found on canvas in the entry called [MDA: Create a repository](https://canvas.ubc.ca/courses/126199/pages/mda-create-a-repository). One completed, your repository should automatically be listed as part of the stat545ubc-2023 Organization.

# Instructions

## For Both Milestones

-   Each milestone has explicit tasks. Tasks that are more challenging will often be allocated more points.

-  Each milestone will be also graded for reproducibility, cleanliness, and coherence of the overall Github submission. 

- While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

- The milestones will be equally weighted. 

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 36 points: 30 for your analysis, and 6 for overall reproducibility, cleanliness, and coherence of the Github submission. 

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset 

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 **(1 point)** Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1. cancer_sample
2. vancouver_trees
3. apt_buildings
4. flow_sample

<!----------------------------------------------------------------------------->

1.2 **(6 points)** One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

#### Cancer sample
The cancer sample (`cancer_sample`) data set was acquired as courtesy of the UCI Machine Learning Repository and comprises patient IDs, diagnosis and 30 other aspects of tumours from `r nrow(cancer_sample)` cancer patients.

```{r}

class(cancer_sample) #this data is structured as a data frame and different tibble variations (tbl, tbl_df, spec_tbl_df)
glimpse(cancer_sample) #this data set has 32 columns (variables)

```
The `cancer_sample` dataset primarily contains rows of patient data and mainly numeric variables that characterize patient tumour features in great depth (ie. radius, texture, perimeter, area, smoothness, compactness, etc.). 


#### Vancouver trees
The Vancouver trees (`vancouver_trees`) data was acquired as courtesy of The City of Vancouver's Open Data Portal and comprises up to 20 specifics about `r nrow(vancouver_trees)` trees in Vancouver.

```{r}

class(vancouver_trees) #this data is structured as a data frame and tibble
glimpse(vancouver_trees) #this data set has 20 columns (variables)

```
The `vancouver_trees` dataset contains a wide variety of information on trees planted in Vancouver area, including features about location, tree type, height, diameter, date planted, etc. Owing to its large size and various types of variables, this dataset would be very informative to learn from!

#### Apartment buildings
The apartment buildings (`apt_buildings`) data was acquired as courtesy of The City of Toronto's Open Data Portal and comprises 37 aspects of apartment listings for `r nrow(apt_buildings)` rental units.

```{r}

class(apt_buildings) #this data is structured as a data frame and tibble (tbl, tbl_df)
glimpse(apt_buildings) #this data set has 37 columns (variables)

```
The `apt_buildings` dataset has detailed apartment information including building amenities, property features such as balcony, window types, year built and registered, etc. At quick glance, some of the categorical variables such as parking type are not standardized in their structure (ie. underground garage vs garage accessible thru building, etc.) so may make analysis challenging. 

#### Flow sample
The flow sample (`flow_sample`) dataset was acquired as courtesy of The Government of Canada's Historical Hydrometric Database and comprises 7 features of flow rate information for `r nrow(flow_sample)` observations.

```{r}

class(flow_sample) #this data is structured as a data frame and tibble (tbl, tbl_df)
glimpse(flow_sample) #this data set has 7 columns (variables)

```
The `flow_sample` dataset is relatively smaller and contains variables that I do not personally recognize as I am unfamiliar with flow data. At quick glance, there also appears to be a lot of missing data, especially in the 'sym' variable which, with an already small dataset, may make analysis challenging.

<!----------------------------------------------------------------------------->

1.3 **(1 point)** Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 1. What lead you to choose this one? Briefly explain your choice below.

<!-------------------------- Start your work below ---------------------------->
While I was initially interested in the cancer_samples dataset as my background and PhD is in immunology and human health, I have decided to explore the vancouver_trees dataset as it contains a variety of variable types (both numeric and categorical data) and is a large dataset. I am hoping to learn how to handle big datasets as I will be working with this type of data during my graduate studies. As a non-BC student, I admire Vancouver's greenery and am interested in exploring more about the various tree species located throughout this beautiful city. I often commute for work and classes between Fairview and UBC campus, so I would be intrigued to use this dataset to visualize more information about the landscape I see while en route on the 99 bus line (and learn more about trees in the process)! 

<!----------------------------------------------------------------------------->

1.4 **(2 points)** Time for a  final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with your dataset. Note it down below.

<!-------------------------- Start your work below ---------------------------->

**Are there patterns to tree planting amongst various communities, between seasons and over time in Vancouver?**

<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset 

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 **(12 points)** Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. 

Make sure that you're using dplyr and ggplot2 rather than base R for this task. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 **(4 points)** For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->
## INTRODUCTION
Hello everyone! To better understand the `vancouver_trees` dataset, we will complete some exercises and dive deeper into the data. Please follow along below as we work through 4 tasks aimed at giving us better insight. We will use the [dplyr](https://dplyr.tidyverse.org/) package to manipulate the data and [ggplot2](https://ggplot2.tidyverse.org/) for data visualization. Ultimately, we hope to address the following question: **Are there patterns to tree planting amongst various communities, between seasons and over time in Vancouver?**

*Let's begin!*

### Investigating and plotting the number of missing values per variable
We will start by exploring how many missing values exist in this dataset as it will give us insight into the quality of the data we are working with. Analyzing which variables have the most missing data is important as missing data may lead to biased conclusions. Additionally, we should be aware that removing rows with missing values may skew our dataset if there are patterns to the missingness (i.e. if dates for all 'x' genus of tree are not indexed, removing rows with missing dates before proceeding with the analysis will make it incorrectly appear as if the 'x' genus of tree is not present in Vancouver). Altogether, exploring and visualizing the number of missing values per variable is a starting place to address the concerns above.

```{r}

# create na_summary tibble that contains variable numbers in one column, counts the number of missing values and calculates the percentage of missing values per variable.
na_summary <- tibble(
  variable = colnames(vancouver_trees),
  num_missing = colSums(is.na(vancouver_trees)),
  perc_missing = num_missing / nrow(vancouver_trees) * 100)

print(na_summary) #lets take a look at the tibble 

# plotting the percentage of missing values
na_summary%>%
  ggplot(aes(x = variable, y = perc_missing)) +
  geom_bar(stat = "identity") +
  xlab("Variables") +
  ylab("Percentage of Missing Values") +
  ggtitle("Percentage of Missing Values Per Variable") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
        axis.text.y = element_text(size = 10))

```

**Note**: If we wanted to only plot variables with missing data, we could first use a filter (such as `filter(perc_missing > 0)`). Since I wanted to visualize the number of variables that have missing data in relation to the total number of variables in the dataset, I decided to not pre-filter the data before plotting.

### Creating a new season variable 
I am interested in investigating how tree planting trends change throughout the year and whether seasonality plays a role. For this reason, it would be valuable to create a new "season" variable. I have defined the seasons as listed in the table below:

Number  | Month   | Season
------  | ------  | --------
1   | January | Winter
2   | February | Winter
3   | March | Spring
4   | April | Spring
5   | May | Spring
6   | June | Summer
7   | July | Summer
8   | August | Summer
9   | September | Fall
10   | October | Fall
11   | November | Fall
12   | December | Winter

```{r}

#creating a new "season" column where the Spring, Summer, Fall or Winter label is assigned to each tree based on the month it was planted
vancouver_trees %>%
  filter(!is.na(date_planted)) %>% 
  mutate(month_planted = month(date_planted),
         season = case_when(
           month_planted %in% c(3, 4, 5) ~ "Spring",
           month_planted %in% c(6, 7, 8) ~ "Summer",
           month_planted %in% c(9, 10, 11) ~ "Fall",
           month_planted %in% c(12, 1, 2) ~ "Winter", 
           TRUE ~ "Unknown")) %>%
  ggplot(aes(x = season)) +
  geom_bar() +
  ggtitle("Number of trees planted during different seasons") +
  xlab("Season") +
  ylab("Number of trees")

```

**Note:** For the exercise above, I did some reading into the case_when() dplyr function which is like the if_else() function briefly mentioned in class. I could have structured the code to have several if_else statements nested in each other, but case_when() allows me to return a particular value (~ " ") if the condition is met (month_planted %in% c(x, y, z)). This function meets the need I have to assign specific season labels based on different month conditions. 

It is interesting to see that the majority of trees included in this dataset are planted in the winter! I had previously heard that fall and spring are good times to plant. Interestingly, the graph above prompted me to look into why planting in colder months would be advantageous and I learned that during winter trees enter dormancy where they conserve their energy in their roots, allowing for them to develop an energy store that permits their prosperous growth during the springtime (see [here](https://lifecyclesproject.ca/2021/11/03/when-is-the-best-time-to-plant-a-fruit-tree/) for more information. Since the ground doesn't freeze over as much in Vancouver like it does in other regions perhaps that's why winter is a popular planting season. I wonder how these patterns would vary in colder and snowy cities such as Calgary... 


### Exploring the distribution of Maple trees (Acer genus) across Vancouver communities

I am also interested in exploring the extent of diversity in the trees planted across different neighborhoods in Vancouver. As the dataset we are working with is quite large, to get a glimpse at potential variability, I will start by plotting the number of Maple trees (my favourite type of tree and a symbol national Canadian identity!) across various Vancouver communities.

```{r}

#plotting the distribution of maple trees (Acer genus) across Vancouver communities
#we need to first group the data by neighbourhood
#then filter to only select and count tees from the Acer genus
acer_count <- vancouver_trees %>%
              group_by(neighbourhood_name) %>%
              filter(genus_name == "ACER") %>%
              summarise(total_trees = n()) 

print(acer_count)

#plotting number of Acer trees in different neighbourhoods 
ggplot(acer_count, aes(x = total_trees, y = neighbourhood_name)) +
  geom_bar(stat = "identity") +
  xlab("Total Acer trees") +
  ylab("") +
  ggtitle("Acer Trees Throughout Vancouver Neighbourhoods ")


```

### Filtering the data to look at species of trees within the Acer genus
In the previous exercise, we explored the number of Maple (Acer) trees across various Vancouver communities. Certain species of Maple trees, particularly the Sugar Maple (Acer saccharum), can be used for their sap to create maple syrup. I am interested in further characterizing the distribution of various species of Maple trees in Vancouver. While I am pretty sure tapping trees within the city is likely illegal, it would be interesting to see whether certain communities have a greater yield of sap (more Sugar Maple trees). The following filtering approach could be modified to look at different tree species, specific neighbourhoods, etc. in subsequent analyses.

```{r fig.width=10, fig.height=20}

#first we want to filter for only Acer trees 
#also we should remove any data where neighbourhood or species name is missing
#then we should group by neighborhood and tree species
#lastly count the number of each species in each neighborhood
species_by_neighborhood <- vancouver_trees %>%
                            filter(genus_name == "ACER" & 
                                    !is.na(neighbourhood_name) & 
                                    !is.na(species_name)) %>%  
                            group_by(neighbourhood_name, species_name) %>%  
                            summarise(count = n()) %>%
                            arrange(desc(count))

print(species_by_neighborhood)

```

Looks like PLATANOIDES and RUBRUM are the most common species of Acer tree across neighbourhoods in Vancouver. We can explore these patterns further in milestone 2!

<!----------------------------------------------------------------------------->

# Task 3: Choose research questions 

**(4 points)** So far, you have chosen a dataset and gotten familiar with it through exploring the data. You have also brainstormed one research question that interested you (Task 1.4).  Now it's time to pick 4 research questions that you would like to explore in Milestone 2! Write the 4 questions and any additional comments below. 

<!--- *****START HERE***** --->

1. **How has the rate of tree planting changed across years?**
2. **How does tree planting correlate with seasonality? Are more trees planted in certain months or seasons?**
3. **Are some neighborhoods more diverse in their range of tree species than others?**
4. **Are certain tree species more prevalent in specific neighborhoods?**

<!----------------------------->

# Overall reproducibility/Cleanliness/Coherence Checklist 

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. An example of a major continuity error is having a data set listed for Task 3 that is not part of one of the data sets listed in Task 1. 

## Error-free code (3 points) 

For full marks, all code in the document should run without error. 1 point deduction if most code runs without error, and 2 points deduction if more than 50% of the code throws an error. 

## Main README (1 point)

There should be a file named `README.md` at the top level of your repository. Its contents should automatically appear when you visit the repository on GitHub.

Minimum contents of the README file:

-   In a sentence or two, explains what this repository is, so that future-you or someone else stumbling on your repository can be oriented to the repository.
-   In a sentence or two (or more??), briefly explains how to engage with the repository. You can assume the person reading knows the material from STAT 545A. Basically, if a visitor to your repository wants to explore your project, what should they know?

Once you get in the habit of making README files, and seeing more README files in other projects, you'll wonder how you ever got by without them! They are tremendously helpful.

## Output (1 point)

All output is readable, recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

(0.5 point deduction if any of the above criteria are not met. 1 point deduction if most or all of the above criteria are not met.)

Our recommendation: right before submission, delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant. Then, after your final commit and push to Github, CHECK on Github to make sure that everything looks the way you intended!

## Tagged release (0.5 points)

You've tagged a release for Milestone 1. 

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.